\MakeUppercase{Notes on Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-04 k-planar.tex
Clearer explanations

We use the partition $(S_x: x\in V(K))$ which generates a graph $H$ with vertex set $V(H)=V(K)$ the edge $xy\in E(H)$ if there exists an edge $vw\in E(H)$ with $v\in S_x$ and $w\in S_y$.

First we argue that this partition has small width, with respect to the layering defined by $T$ (note that this is a layering of $G^+$, not a layering of $G$).

@@

Next we describe a tree decomposition $(B_x:x\in V(K))$ of $H$.  (Don't be put off here by the fact that $V(H)=V(K)$).  We claim that, for every edge $xz\in V(H)$, $x$ is an ancestor of $z$ (or vice-versa).  Indeed, this follows from the same argument used to show that $S_x$ is a partition.  If neither $x$ nor $z$ is an ancestor of the other, then any edge $vw$ with $v\in S_x$ and $w\in S_z$ contains a vertex of $Y_a$ for some common ancestor $a$ of $x$ and $z$.

>>>>

We use the partition $(S_x: x\in V(K))$ which generates a graph $H$ with vertex set $V(H)=V(K)$ the edge $xy\in E(H)$ if there exists an edge $vw\in E(H)$ with $v\in S_x$ and $w\in S_y$.
First we argue that this partition has small width with respect to the layering defined by $T$ (note that this is a layering of $G^+$, not a layering of $G$).

@@

Next we describe a tree decomposition $(B_x:x\in V(K))$ of $H$.  (Don't be put off here by the fact that $V(H)=V(K)$, this is actually helpful because the subtree $K[x]$ will be rooted at $x$).  We claim that, for every edge $xz\in V(H)$, $x$ is an ancestor of $z$ (or vice-versa).  Indeed, this follows from the same argument used to show that $S_x$ is a partition.  If neither $x$ nor $z$ is an ancestor of the other, then any edge $vw$ with $v\in S_x$ and $w\in S_z$ contains a vertex of $Y_a$ for some common ancestor $a$ of $x$ and $z$. But this implies that neither $v$ nor $w$ appears in $S_x$ nor $S_z$.
